---
title: "Conference Word Analysis"
author: "Kameron York"
date: "2023-11-07"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
library(tidyverse)
library(pander)
library(plotly)
library(DT)
library(latticeExtra)
library(stringr)

```

```{r, include=FALSE}
# Loading in the Data
talks_data <- read.csv("https://www.kameronyork.com/datasets/general-conference-talks.csv", encoding="UTF-8")
dedication_data <- read.csv("https://www.kameronyork.com/datasets/dedication-data.csv", encoding="UTF-8") %>% 
  mutate(year = str_sub(dedicated, 0, 4))
```

```{r, include=FALSE}
# Loading in the quotes data
quotes <- read.csv("https://www.kameronyork.com/datasets/conference-quotes.csv", encoding="UTF-8")
```

# Can a Prophet Effect a Change? {.tabset .tabset-pills}

## Temples: {.tabset}
("Temple", "Temples", "House of God", "House of the Lord")
```{r, message=FALSE}
# Create a new column to count occurrences of the specified words
temple_data <- talks_data %>%
  mutate(
    temple_count = str_count(tolower(text), "\\btemple\\b"),
    temples_count = str_count(tolower(text), "\\btemples\\b"),
    house_of_the_lord_count = str_count(tolower(text), "\\bhouse of the lord\\b"),
    house_of_god_count = str_count(tolower(text), "\\bhouse of god\\b")
  ) %>% 
  mutate(
    total_temple = temple_count + temples_count + house_of_the_lord_count + house_of_god_count
  )

```

### Scatter Plots
This plot shows there seems to be an increase in temple-related words following President Hinckley's sustaining as prophet.  The large gap in the middle is due to the sudden jump from 63 temples in 1999 to 102 temples in 2000.  There are no dots through that section because no General Conference addresses were given in that time frame.
```{r, warning=FALSE, message=FALSE}
temple_by_year <- temple_data %>% 
  group_by(year) %>% 
  summarise(total = sum(total_temple)) %>% 
  mutate(temples = map_int(year, ~ sum(dedication_data$year <= .x)))

# ggplot(data = temple_by_year) +
#   geom_point(mapping = aes(x = year, y = total), color = "forestgreen") +
#   geom_vline(xintercept = 1995, color = "red") +
#   theme_bw() +
#   labs(
#     title = "Use of Temple Related Words in General Conference Talks",
#     subtitle = "1995 Highlighted - Year President Gordon B. Hinckley became Church President",
#     caption = '"Temple", "House of God", "House of the Lord"',
#     x = "Year",
#     y = "Mentions of the Temple"
#   )

ggplot(data = temple_by_year) +
  geom_point(mapping = aes(x = temples, y = total), color = "forestgreen") +
  geom_vline(xintercept = 47, color = "red") +
  theme_bw() +
  labs(
    title = "Use of Temple Related Words in General Conference Talks",
    subtitle = "1995 Highlighted - Year President Gordon B. Hinckley became Church President",
    caption = '"Temple", "Temples", "House of God", "House of the Lord"',
    x = "Number of Dedicated Temples",
    y = "Mentions of the Temple"
  )
```

This plot shows the number of temples in the world by year:
```{r, warning=FALSE, message=FALSE}
ggplot(data = temple_by_year) +
  geom_point(mapping = aes(x = year, y = temples), color = "forestgreen", size = 1) +
  geom_line(mapping = aes(x = year, y = temples), color = "forestgreen") +
  theme_bw() +
  labs(
    title = "Number of Temples in the World by Year",
    subtitle = "Data is representing the count of dedicated temples at the end of the year",
    x = "Year",
    y = "Number of Dedicated Temples"
  )
```

This time the phrases are shown in different colors.
```{r, warning=FALSE, message=FALSE}
temple_pivot <- temple_data %>% 
  select(year, speaker, title, temple_count, temples_count, house_of_the_lord_count, house_of_god_count) %>% 
  pivot_longer(
    cols = c(temple_count, temples_count, house_of_the_lord_count, house_of_god_count),
    names_to = "type",
    values_to = "count"
  ) %>% 
  group_by(year, type) %>% 
  summarise("total" = sum(count))

ggplot(data = temple_pivot) +
  geom_point(mapping = aes(x = year, y = total, color = type)) +
  geom_vline(xintercept = 1995, color = "red") +
  theme_bw() +
  labs(
    title = "Use of Temple Related Words in General Conference Talks",
    subtitle = "1995 Highlighted - Year President Gordon B. Hinckley became Church President",
    caption = '"Temple", "Temples", "House of God", "House of the Lord"',
    color = "Mention Type",
    x = "Year",
    y = "Mentions of the Temple"
  )
```



### Box Plot
This boxplot shows that there is an increase in temple-related words between before President Hinckley was the prophet and our current Post-President Hinckley era.  It seems temples are being talked about more now than they were before his sustaining. 
```{r, warning=FALSE, message=FALSE}
temple_boxes <- temple_by_year %>% 
  mutate(group = case_when(
    year < 1995 ~ "Before Hinckley",
    year >= 1995 ~ "Post Hinckley"
  ))


ggplot(data = temple_boxes) + 
  geom_boxplot(mapping = aes(x = group, y = total)) + 
  theme_bw()
```

### T Test

```{r, warning=FALSE, message=FALSE}
t.test(total ~ group, data = temple_boxes, mu = 0, alternative = "two.sided", conf.level = 0.95) %>% 
  pander()
```

### Wilcoxon Test

```{r, warning=FALSE, message=FALSE}
wilcox.test(total ~ group, data = temple_boxes, mu = 0, alternative = "two.sided", conf.level = 0.95) %>% 
  pander()

```


## Book of Mormon: {.tabset}
("Book of Mormon")
```{r, warning=FALSE, message=FALSE}
bom_data <- talks_data %>%
  mutate(
    total_bom = str_count(tolower(text), "(?i)\\bbook of mormon\\b")
  )
```


### Scatter Plots

```{r, warning=FALSE, message=FALSE}
bom_by_year <- bom_data %>% 
  group_by(year) %>% 
  summarise(total = sum(total_bom))

ggplot(data = bom_by_year) +
  geom_point(mapping = aes(x = year, y = total), color = "forestgreen") +
  geom_vline(xintercept = 1986, color = "red") +
  theme_bw() +
  labs(
    title = "Use of Book of Mormon Related Words in General Conference Talks",
    subtitle = "1986 Highlighted - Year President Ezra Taft Benson Reaffirmed the Book of Mormon",
    caption = '"Book of Mormon"',
    x = "Year",
    y = "Mentions of the Book of Mormon"
  )

```

Are the scriptures from the book of mormon quoted more now than in the 70's before the talk?
```{r, warning=FALSE, message=FALSE}
bom_quotes <- quotes %>% 
  filter(overall_book == "Book of Mormon") %>% 
  group_by(talk_year) %>% 
  summarise(total = n())

ggplot(data = bom_quotes, aes(x = talk_year, y = total)) + 
  geom_point(color = "red2") + 
  geom_smooth(method = lm, se = FALSE, color = "orange", linetype = "solid") +
  geom_vline(xintercept = 1986, color = "blue3") +
  theme_bw() +
  labs(
    title = "Quotes from the Book of Mormon in General Conference Talks",
    subtitle = "1986 Highlighted - Year President Ezra Taft Benson Reaffirmed the Book of Mormon",
    caption = '"Book of Mormon"',
    x = "Year",
    y = "Quotes from the Book of Mormon"
  )

```


```{r, warning=FALSE, message=FALSE}
mylm <- lm(total ~ talk_year, data = bom_quotes)
summary(mylm) %>% 
  pander()
```

### Box Plot

```{r, warning=FALSE, message=FALSE}
bom_boxes <- bom_quotes %>% 
  mutate(group = case_when(
    talk_year < 1986 ~ "Before Talk", 
    talk_year >= 1986 ~ "Post Talk"
  ))

bom_means <- bom_boxes %>% 
  group_by(group) %>% 
  summarise(mean = mean(total))

ggplot(data = bom_boxes) + 
  geom_boxplot(mapping = aes(x = group, y = total)) + 
  geom_point(data = bom_means, mapping = aes(x = group, y = mean), color = "red3") +
  theme_bw()

```   

### T Test

```{r, warning=FALSE, message=FALSE}
t.test(total ~ group, data = bom_boxes, mu = 0, alternative = "two.sided", conf.level = 0.95) %>% 
  pander()
```


### Wilcoxon Test

```{r, warning=FALSE, message=FALSE}
wilcox.test(total ~ group, data = bom_boxes, mu = 0, alternative = "two.sided", conf.level = 0.95) %>% 
  pander()

```

### Bible Comparison

```{r, warning=FALSE, message=FALSE}
bible_compare <- quotes %>% 
  filter(overall_book %in% c("Book of Mormon", "Bible")) %>% 
  group_by(talk_year, overall_book) %>% 
  summarise(total = n())

ggplot(data  = bible_compare) + 
  geom_point(mapping = aes(x = talk_year, y = total, color = overall_book)) + 
  geom_smooth(se = FALSE, mapping = aes(x = talk_year, y = total, color = overall_book)) + 
  theme_bw()

```

Is there a difference in boxplots Pre President Benson and Post President Benson?
```{r, warning=FALSE, message=FALSE}
benson_check <- bible_compare %>% 
  mutate(group = case_when(
    talk_year < 1986 ~ "Before Talk",
    talk_year >= 1986 ~ "Post Talk"
  )) %>% 
  mutate(overall_group = paste(overall_book, group, sep = " - "))

ggplot(data = benson_check) + 
  geom_boxplot(mapping = aes(x = overall_group, y = total, fill = overall_book)) + 
  theme_bw()

```


## Gathering Israel {.tabset}
("Gathering Israel", "Both Sides of the Veil")

### Scatter Plots

```{r, warning=FALSE, message=FALSE}
gathering_data <- talks_data %>%
  mutate(
    gathering1 = str_count(tolower(text), "(?i)\\bgathering of israel\\b"),
    gathering2 = str_count(tolower(text), "(?i)\\bgathering israel\\b"),
    both_sides = str_count(tolower(text), "(?i)\\bboth sides of the veil\\b")
  ) %>% 
  mutate(gathering = gathering1 + gathering2)
  
gathering_pivot <- gathering_data %>% 
  select(year, speaker, title, gathering, both_sides) %>% 
  pivot_longer(
    cols = c(gathering, both_sides),
    names_to = "type",
    values_to = "count"
  ) %>% 
  group_by(year, type) %>% 
  summarise("total" = sum(count)) %>% 
  mutate(group = case_when(
    year < 2017 ~ "Before Nelson",
    year >= 2017 ~ "Post Nelson"
  ))

ggplot(data = gathering_pivot) +
  geom_point(mapping = aes(x = year, y = total, color = type)) +
  geom_smooth(se = FALSE, mapping = aes(x = year, y = total, color = type)) + 
  geom_vline(xintercept = 2017, color = "red") +
  theme_bw() +
  labs(
    title = "Use of Gathering Israel Related Words in General Conference Talks",
    subtitle = "2017 Highlighted - President Nelson sustained as Prophet",
    caption = '"Gathering Israel", "Both Sides of the Veil"',
    color = "Mention Type",
    x = "Year",
    y = "Mentions of Gathering Israel"
  )
```

### Box Plot

```{r, warning=FALSE, message=FALSE}

gathering_means <- gathering_pivot %>% 
  group_by(group) %>% 
  summarise(mean = mean(total))

ggplot(data = gathering_pivot) + 
  geom_boxplot(mapping = aes(x = group, y = total)) + 
  geom_point(data = gathering_means, mapping = aes(x = group, y = mean), color = "red3") +
  theme_bw()

```   

### T Test

```{r, warning=FALSE, message=FALSE}
t.test(total ~ group, data = gathering_pivot, mu = 0, alternative = "two.sided", conf.level = 0.95) %>% 
  pander()
```


### Wilcoxon Test

```{r, warning=FALSE, message=FALSE}
wilcox.test(total ~ group, data = gathering_pivot, mu = 0, alternative = "two.sided", conf.level = 0.95) %>% 
  pander()

```


# Other Insights {.tabset .tabset-pills}

## Missionary Work
("Missionary", "Missionaries", "Every member a missionary")

```{r, warning=FALSE, message=FALSE}
missionary_data <- talks_data %>%
  mutate(
    missionary = str_count(tolower(text), "(?i)\\bmissionary\\b"),
    missionaries = str_count(tolower(text), "(?i)\\bmissionaries\\b")
  )
  
missionary_pivot <- missionary_data %>% 
  select(year, speaker, title, missionary, missionaries) %>% 
  pivot_longer(
    cols = c(missionary, missionaries),
    names_to = "type",
    values_to = "count"
  ) %>% 
  group_by(year, type) %>% 
  summarise("total" = sum(count))


ggplot(data = missionary_pivot) +
  geom_point(mapping = aes(x = year, y = total, color = type)) +
  geom_smooth(mapping = aes(x = year, y = total)) + 
  geom_vline(xintercept = 1974, color = "red") +
  theme_bw() +
  labs(
    title = "Use of Temple Related Words in General Conference Talks",
    subtitle = "1974 Highlighted - Release of 'Go ye into all the World' by President Kimball",
    caption = '"Missionary", "Missionaries", "Every Member a Missionary"',
    color = "Mention Type",
    x = "Year",
    y = "Mentions of the Temple"
  )

```


## Family History and Genealogy
("Family History", "Genealogy")

```{r, warning=FALSE, message=FALSE}
family_search_data <- talks_data %>%
  mutate(
    family_history = str_count(tolower(text), "(?i)\\bfamily history\\b"),
    genealogy = str_count(tolower(text), "(?i)\\bgenealogy\\b")
  )
  
family_pivot <- family_search_data %>% 
  select(year, speaker, title, family_history, genealogy) %>% 
  pivot_longer(
    cols = c(family_history, genealogy),
    names_to = "type",
    values_to = "count"
  ) %>% 
  group_by(year, type) %>% 
  summarise("total" = sum(count))

ggplot(data = family_pivot) +
  geom_point(mapping = aes(x = year, y = total, color = type)) +
  geom_smooth(se = FALSE, mapping = aes(x = year, y = total, color = type)) + 
  geom_vline(xintercept = 1974, color = "red") +
  theme_bw() +
  labs(
    title = "Use of Temple Related Words in General Conference Talks",
    subtitle = "1974 Highlighted - Release of 'Go ye into all the World' by President Kimball",
    caption = '"Missionary", "Missionaries", "Every Member a Missionary"',
    color = "Mention Type",
    x = "Year",
    y = "Mentions of the Temple"
  )
```

## Gospel of Jesus Christ
("Faith", "Repentance", "Baptism", "Gift of the Holy Ghost", "Endure to the End")

```{r, warning=FALSE, message=FALSE}
gospel_principles <- talks_data %>%
  mutate(
    faith = str_count(tolower(text), "(?i)\\bfaith\\b"),
    repentance = str_count(tolower(text), "(?i)\\brepentance\\b"),
    baptism = str_count(tolower(text), "(?i)\\bbaptism\\b"),
    holy_ghost = str_count(tolower(text), "(?i)\\bgift of the holy ghost\\b"),
    endure = str_count(tolower(text), "(?i)\\bendure to the end\\b"),
  )
  
gospel_pivot <- gospel_principles %>% 
  select(year, speaker, title, faith, repentance, baptism, holy_ghost, endure) %>% 
  pivot_longer(
    cols = c(faith, repentance, baptism, holy_ghost, endure),
    names_to = "type",
    values_to = "count"
  ) %>% 
  group_by(year, type) %>% 
  summarise("total" = sum(count))

ggplot(data = gospel_pivot) +
  geom_point(mapping = aes(x = year, y = total, color = type)) +
  geom_smooth(se = FALSE, mapping = aes(x = year, y = total, color = type)) + 
  geom_vline(xintercept = 2008, color = "red") +
  theme_bw() +
  labs(
    title = "Use of Temple Related Words in General Conference Talks",
    subtitle = "1974 Highlighted - Release of 'Go ye into all the World' by President Kimball",
    caption = '"Missionary", "Missionaries", "Every Member a Missionary"',
    color = "Mention Type",
    x = "Year",
    y = "Mentions of the Temple"
  )
```

```{r, warning=FALSE, message=FALSE}
ggplot(data = filter(gospel_pivot, type != "faith")) +
  geom_point(mapping = aes(x = year, y = total, color = type)) +
  geom_smooth(se = FALSE, mapping = aes(x = year, y = total, color = type)) + 
  geom_vline(xintercept = 2008, color = "red") +
  theme_bw() +
  labs(
    title = "Use of Temple Related Words in General Conference Talks",
    subtitle = "1974 Highlighted - Release of 'Go ye into all the World' by President Kimball",
    caption = '"Missionary", "Missionaries", "Every Member a Missionary"',
    color = "Mention Type",
    x = "Year",
    y = "Mentions of the Temple"
  )

```

```{r, warning=FALSE, message=FALSE}
gospel_principles <- talks_data %>%
  mutate(
    gospel = str_count(tolower(text), "(?i)\\bgospel of jesus christ\\b")
  )
  
gospel_pivot <- gospel_principles %>% 
  select(year, speaker, title, gospel) %>% 
  pivot_longer(
    cols = c(gospel),
    names_to = "type",
    values_to = "count"
  ) %>% 
  group_by(year, type) %>% 
  summarise("total" = sum(count))

ggplot(data = gospel_pivot) +
  geom_point(mapping = aes(x = year, y = total)) +
  geom_smooth(se = FALSE, mapping = aes(x = year, y = total)) + 
  geom_vline(xintercept = 2008, color = "red") +
  theme_bw() +
  labs(
    title = "Use of the Phrase 'Gospel of Jesus Christ' in General Conference Talks",
    # subtitle = "1974 Highlighted - Release of 'Go ye into all the World' by President Kimball",
    caption = '"Gospel of Jesus Christ"',
    x = "Year",
    y = "Mentions of the Temple"
  )
```


<!-- ## Pornography -->
<!-- ("pornography", "porn") -->
<!-- ```{r} -->
<!-- # Create a new column to count occurrences of the specified words -->
<!-- p_data <- talks_data %>% -->
<!--   mutate( -->
<!--     pornography = str_count(tolower(text), "\\bpornography\\b"), -->
<!--     porn = str_count(tolower(text), "\\bporn\\b") -->
<!--   ) %>%  -->
<!--   mutate( -->
<!--     total_p  = pornography + porn -->
<!--   ) %>%  -->
<!--   mutate(total_p = ifelse(is.na(total_p), 0, total_p)) -->

<!-- p_by_year <- p_data %>%  -->
<!--   group_by(year) %>%  -->
<!--   summarise(total = sum(total_p)) -->

<!-- ggplot(data = p_by_year) + -->
<!--   geom_point(mapping = aes(x = year, y = total), color = "forestgreen") + -->
<!--   theme_bw() + -->
<!--   labs( -->
<!--     title = "Use of Pornography Related Words in General Conference Talks", -->
<!--     caption = '"Pornography", "Porn"', -->
<!--     x = "Year", -->
<!--     y = "Mentions of Pornography" -->
<!--   ) -->

<!-- ``` -->





